\documentclass[11pt]{article}

\usepackage{amsmath,amssymb}
\usepackage{xurl}
\usepackage[hidelinks]{hyperref}
\setlength{\emergencystretch}{2em}

\input{command}

\title{The Support of the Distinct-Tuple Distribution}
\author{}
\date{2026-05-01}

\begin{document}
\maketitle

\section{The assertion}

This note concerns the distinct-tuple distribution used in the pasting section of
\cite{Ji2020LowIndividualDegree}.%
\footnote{Tracked as part of the discrepancy audit in \ghissue{930}.  In the
TeX source consulted here, the definition and comparison proposition are in
\path{references/ldt-paper/ld-pasting.tex}, lines~167--213.}
For $k\ge 1$, the paper defines
\[
  \mathsf{Distinct}_k=\{(x_1,\ldots,x_k)\in \F_q^k: x_i\ne x_j
    \text{ for }i\ne j\}
\]
and writes $(\mathbf y_1,\ldots,\mathbf y_k)\sim \mathsf{Distinct}_k$ for a uniformly
random element of this set.  The following comparison proposition then bounds
the total variation distance between a uniformly random tuple in $\F_q^k$ and a
uniformly random tuple in $\mathsf{Distinct}_k$ by $k^2/q$.

\section{The point at issue}

The distribution on $\mathsf{Distinct}_k$ is a genuine probability distribution only
when $\mathsf{Distinct}_k$ is nonempty.  This requires $k\le q$.  The statement of the
comparison proposition and the surrounding pasting theorem do not state this
condition.  Later in the section the paper assumes $k\ge 400md$, but it does
not separately assume $k\le q$.

Thus, read literally, the phrase ``uniformly random element of
$\mathsf{Distinct}_k$'' is undefined in the case $k>q$.  In that case no injective map
from $\{1,\ldots,k\}$ to $\F_q$ exists.  The displayed bound $k^2/q$ is then
already at least $1$, so the intended comparison is only used in a regime where
the estimate is trivial, but the probability distribution itself still needs a
formal interpretation.

\section{The blueprint statement}

The blueprint repeats the paper's convention rather than making the boundary
case explicit.  The node \path{def:distinct-tuples} in
\path{blueprint/src/chapter/ch09_pasting.tex}, lines~198--202, carries
\verb|\lean| annotations for \path{MIPStarRE.LDT.Pasting.distinctTuples} and
\path{MIPStarRE.LDT.Pasting.distinctTupleDistribution}, together with
\verb|\leanok|, and states: ``For $k\ge 1$, let
$\mathsf{Distinct}_k\subseteq \F_q^k$ be the set of tuples
$(x_1,\dots,x_k)$ with pairwise distinct coordinates.''  This is the same
all-$k\ge 1$ convention as the paper; the blueprint definition does not add the
missing nonemptiness hypothesis $k\le q$.

The companion node \path{prop:ld-dnoteq} in the same file, lines~204--226, has a
\verb|\lean| annotation for \path{MIPStarRE.LDT.Pasting.ldDnoteq} and is also
tagged \verb|\leanok|.
It states that if $x=(x_1,\dots,x_k)$ is uniformly random in $\F_q^k$ and
$y=(y_1,\dots,y_k)$ is uniformly random in $\mathsf{Distinct}_k$, then
$d_{\mathrm{TV}}(x,y)\le k^2/q$.  Again, the blueprint records no $k\le q$
side condition for the phrase ``uniformly random in $\mathsf{Distinct}_k$''.

Thus the Lean repair is invisible from the blueprint side: a reader following
the formalized blueprint nodes sees the same probability-language statement as
in the paper, while the checked Lean declarations below implement the total
object as a finite nonnegative weight for all $k$ and recover a probability
interpretation only when the support is nonempty, equivalently when $k\le q$.

\section{The formal repair}

The formal development uses a finite-support weighted distribution rather than
forcing every distribution object to be normalized.  The declaration
\path{MIPStarRE.LDT.Pasting.distinctTupleDistribution} assigns weight
$1/|\mathsf{Distinct}_k|$ to each distinct tuple when the support is nonempty, and
weight zero outside the support.  If $k>q$, the support is empty, so this is the
zero finite measure rather than a probability distribution.%
\footnote{See \doclink{MIPStarRE/LDT/Pasting/Defs/Tuples.lean}, lines~23--36.}

The formalization records both facts.  The general theorem
\path{MIPStarRE.LDT.Pasting.distinctTupleDistribution_weight_sum_le_one}
proves that the total mass is at most $1$ for every $k$.  The normalized form
\path{MIPStarRE.LDT.Pasting.distinctTupleDistribution_weight_sum_eq_one_of_le}
adds the missing hypothesis $k\le q$ and proves that the total mass is exactly
$1$.%
\footnote{The normalized statement is in
\doclink{MIPStarRE/LDT/Pasting/BridgeLemmas/Common.lean}, lines~311--343 of the
source file.}

The total-variation comparison
\path{MIPStarRE.LDT.Pasting.ldDnoteq} is correspondingly case-split.  When
$k\le q$, it proves the usual collision-probability estimate.  When $k>q$, the
support is empty; the formal total variation between the uniform tuple
distribution and the zero distinct-tuple weight is $1/2$, and this is bounded
by $k^2/q$ because $k>q$.%
\footnote{See \doclink{MIPStarRE/LDT/Pasting/Core.lean}, lines~561--805.}
Downstream averaging lemmas use the same convention: they compare expectations
of nonnegative functions bounded by $1$, and the $k>q$ branch is discharged by
the now-trivial $k^2/q$ error term.

\section{Conclusion}

The paper implicitly treats the distinct-tuple distribution as if it were
available for all $k\ge 1$.  A literal probability distribution exists only for
$k\le q$.  The formal development makes the boundary case total by interpreting
the distinct-tuple object as a finite nonnegative weight for all $k$, and as a
probability distribution precisely under the additional hypothesis $k\le q$.
This is a harmless formal repair: it preserves the paper argument in the
nonempty-support case and makes the empty-support case a trivial bound rather
than an undefined sampling operation.

\bibliographystyle{alpha}
\bibliography{references}

\end{document}
