\documentclass{article}

\usepackage{amsmath,amssymb}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\setlength{\emergencystretch}{2em}

\input{./command}

\title{The Constant in the Completion-Route Orthonormalization Theorem}
\author{}
\date{2026-05-11}

\begin{document}
\maketitle

\section{At a glance}

This note concerns the constant in the Section~5 orthonormalization theorem of
\cite{Ji2020LowIndividualDegree}.

\begin{itemize}
  \item \textbf{Difficulty.} Medium.  The discrepancy is a scalar loss, but
  recovering the paper constant requires aligning the local repair lemma with
  the bipartite self-consistency hypothesis used in the source proof.
  \item \textbf{Estimated weight.} One reformulated repair theorem, with a
  moderate amount of project-local scalar and transport work.
  \item \textbf{Mathlib/project split.} Mostly project-local; Mathlib supplies
  the elementary real-power inequalities and matrix order infrastructure.
  \item \textbf{Key mathematical inputs.} The Section~5 completion step, the conversion from
  consistency to almost-projectivity, and the local \(Q/X/\widehat X/P\) repair
  theorem.
\end{itemize}

\section{Key theorem forms}

Throughout, \(\ket{\psi}\) denotes a normalized bipartite state on
\(\mathcal H_A\otimes\mathcal H_A\), \(A=\{A_a\}_{a\in\mathcal A}\)
is a submeasurement on \(\mathcal H_A\) with strong self-consistency error
\(\zeta\ge 0\), and \(P=\{P_a\}_{a\in\mathcal A}\) is a projective
submeasurement on \(\mathcal H_A\).  The relation
\(\{X_a\}\approx_\delta\{Y_a\}\), in the tensor-placement used here, abbreviates
the state-dependent squared-distance estimate
\[
  \sum_a
  \bra{\psi}
    (X_a\otimes I-Y_a\otimes I)^\dagger
    (X_a\otimes I-Y_a\otimes I)
  \ket{\psi}
  \le \delta.
\]

The paper states the orthonormalization theorem with the estimate
\[
  A_a \otimes I \approx_{100\zeta^{1/4}} P_a \otimes I.
\]
The Lean declaration named
\(\leanid{MIPStarRE.LDT.MakingMeasurementsProjective.orthonormalization}\)
now proves this paper statement and its axiom audit requires only the standard
Lean axioms.
The proved completion-route theorem
\(\leanid{MIPStarRE.LDT.MakingMeasurementsProjective.orthonormalizationCompletionRoute}\)
establishes the same conclusion with the weaker estimate
\[
  A_a \otimes I \approx_{120\zeta^{1/4}} P_a \otimes I.
\]
The earlier input-driven theorem, in which the stronger repair input was
supplied separately, has been removed from the public Section 5 API; the
corresponding statement is now represented by the paper-facing theorem together
with a separate proved completion-route comparison.%
\footnote{The source theorem is
\path{references/ldt-paper/orthonormalization.tex:67-75}
(\path{thm:orthonormalization}).  The relevant declarations are
\leanid{MIPStarRE.LDT.MakingMeasurementsProjective.orthonormalization},
\leanid{MIPStarRE.LDT.MakingMeasurementsProjective.orthonormalizationCompletionRoute},
and \leanid{MIPStarRE.LDT.MakingMeasurementsProjective.leftLiftedProjectivizationRepair\_of\_sourceAlmostProjective\_two\_mul}.
This note is attached to \ghissue{1032}; the constant discrepancy is resolved
by proving the source-aligned theorem statement.  The heterogeneous
\path{lem:orthonormalization-main-lemma} proof remains a separate tracked
obligation, but the public orthonormalization theorem no longer depends on that
unfinished lemma.  The weaker completion-route construction stays under a
separate name.}

\section{The source assertion}

In the source proof of the orthonormalization lemma, the submeasurement \(A\)
is first completed to a measurement \(\widehat A\) on
\(\mathcal A\cup\{\bot\}\), by setting \(\widehat A_a=A_a\) for
\(a\in\mathcal A\) and
\(\widehat A_\bot=I-\sum_{a\in\mathcal A} A_a\).  The completed measurement
has bipartite strong self-consistency error \(2\zeta\).  The paper then applies
the main orthonormalization lemma directly at this error level.  The relevant
source passages are the main lemma statement at
\path{references/ldt-paper/orthonormalization.tex:282-293}
(\path{lem:orthonormalization-main-lemma}) and the completion-and-apply
argument at \path{references/ldt-paper/orthonormalization.tex:304-369}.
This gives
\[
  \widehat A_a \otimes I
    \approx_{84(2\zeta)^{1/4}}
  \widehat P_a \otimes I.
\]
The displayed estimate occurs at line \(358\), and the closing scalar
calculation \(84\cdot 2^{1/4}\simeq 99.89 \le 100\) occurs at line \(368\).
Thus the paper obtains the stated \(100\zeta^{1/4}\) bound after
discarding the completion outcome.

\section{Comparison with the formalization}

The proved completion-route theorem follows a slightly different route.  After
completion it converts the \(2\zeta\) self-consistency estimate into a
source-almost-projective estimate before invoking the locality-preserving
\(Q/X/\widehat X/P\) repair theorem.  This route is recorded by the named
Lean declaration
\(\leanid{MIPStarRE.LDT.MakingMeasurementsProjective.orthonormalizationCompletionRoute}\)
and the error function
\(\mathsf{orthonormalizationCompletionRouteError}(\zeta)=120\zeta^{1/4}\).
The conversion doubles the scalar:
\[
  \operatorname{consistencyToAlmostProjectiveError}(2\zeta)=4\zeta.
\]
The local repair theorem then gives
\[
  84(4\zeta)^{1/4}
    = 84\cdot 4^{1/4}\zeta^{1/4}
    \le 120\zeta^{1/4}.
\]
Thus the completion-route theorem has the same mathematical shape as the paper
theorem, but its constant is weaker by the extra factor \(2^{1/4}\) introduced
by this conversion step.  It is kept as useful proof content, but it is no
longer the declaration presented as the paper theorem.

\section{Conclusion}

The scalar constant discrepancy in the completion-to-measurement route has been
removed from the statement of
\(\leanid{MIPStarRE.LDT.MakingMeasurementsProjective.orthonormalization}\).
The formal proof follows the paper's completion-to-measurement reduction and
then uses a sharp locality-preserving repair route at the correct \(2\zeta\)
scale, avoiding the extra factor introduced by the historical completion-route
proof.  The weaker completion-route theorem remains available under the
separate name
\(\leanid{MIPStarRE.LDT.MakingMeasurementsProjective.orthonormalizationCompletionRoute}\).

This does not close every Section~5 proof obligation.  The heterogeneous
\(\leanid{MIPStarRE.LDT.MakingMeasurementsProjective.orthonormalizationMainLemma}\)
still remains as a tracked \texttt{sorry}; it should either be proved directly
from the paper argument or kept unmarked as an unfinished auxiliary lemma.  The
public theorem
\(\leanid{MIPStarRE.LDT.MakingMeasurementsProjective.orthonormalization}\)
does not depend on that unfinished lemma, and its scalar constant is now the
paper constant.

\bibliographystyle{alpha}
\bibliography{references}

\end{document}
