\documentclass[11pt]{article}

\usepackage{amsmath,amssymb}
\usepackage{xurl}
\usepackage[hidelinks]{hyperref}
\setlength{\emergencystretch}{2em}

\input{command}

\title{The Large-\texorpdfstring{$k$}{k} Side Condition in the Main Induction}
\author{}
\date{2026-04-29}

\begin{document}
\maketitle

\section{At a glance}

\begin{itemize}
  \item \textbf{Difficulty: medium.}  The issue is not a missing analytic
  estimate, but a mismatch between the size hypothesis printed in the paper and
  the size hypothesis consumed by the present pasting route.
  \item \textbf{Estimated weight:} about \textbf{3--6 scalar or boundary
  lemmas} if one proves a smaller-\(k\) saturation argument, or a theorem-level
  correction if the present large-\(k\) route is retained.
  \item \textbf{Mathlib/project split:} approximately \textbf{10\% Mathlib} and
  \textbf{90\% project-local}.  The arithmetic is elementary; the substance is
  deciding which LDT theorem statement is justified by the paper's pasting
  pipeline.
  \item \textbf{Key Mathlib inputs:} elementary order arithmetic on natural
  numbers and nonnegative real error parameters.  The main inputs are the
  project-local statements of the main induction, pasting, and final scalar
  cascade.  Tracked in \ghissue{906}.
\end{itemize}

\section{Key theorem forms}

The comparison involves three theorem forms.
\begin{enumerate}
  \item \textbf{Printed source form.}  The theorem in
  \path{references/ldt-paper/inductive_step.tex} assumes \(k\ge md\), and its
  successor proof assumes \(k\ge (m+1)d\).
  \item \textbf{Pasting-input form.}  The pasting theorem used in the successor
  proof requires \(k\ge 400md\) in the restricted \(m\)-dimensional slice.
  \item \textbf{Current formal-interface form.}  The Lean theorem
  \leanid{MIPStarRE.LDT.MainInductionStep.mainInduction} and the final theorem
  \leanid{MIPStarRE.LDT.Test.mainFormal} use the corrected large-\(k\)
  interface, displayed in the blueprint as separate current-interface entries.
\end{enumerate}

\section{The assertion}

This note concerns the \(k\)-hypothesis in the main induction theorem of
\cite[Section~\emph{The main induction step}]{Ji2020LowIndividualDegree}, and
its use in the proof of the main formal soundness theorem.
\footnote{The original discrepancy was recorded in \ghissue{906} and first
implemented in \ghpr{912}.  The documentation issue for this note is
\ghissue{928}.  In the TeX source consulted here, the main induction theorem is in
\path{references/ldt-paper/inductive_step.tex}, lines 7--18; the successor step
is in the same file, lines 429--568; and the pasting theorem used there is in
lines 299--330.}
Here \(m\) is the number of variables, \(q\) is the field size, \(d\) is the
individual degree bound, and \(k\) is the sampling parameter in the consistency
estimates.  The integer \(k\) is carried unchanged through the induction on
\(m\).

In the theorem as stated, an \((\varepsilon,\delta,\gamma)\)-good symmetric
strategy for the \((m,q,d)\) low individual degree test is assumed to satisfy
only
\begin{equation*}
  k\ge md.
  \tag{\path{thm:main-induction}}
\end{equation*}
Under this hypothesis, the theorem produces a polynomial measurement
\(G\in\operatorname{PolyMeas}(m,q,d)\) satisfying the advertised consistency
estimate.  The same \(k\)-condition is then inherited by the stated main formal
soundness theorem after the reduction from a general two-prover strategy to a
symmetric one.

\section{The use of pasting}

The successor step proves the induction theorem in dimension \(m+1\) assuming
the theorem in dimension \(m\).  In that step the ambient strategy is a strategy
for the \((m+1,q,d)\) test, and the proof assumes
\begin{equation*}
  k\ge (m+1)d.
  \tag{\path{sec:proof-of-main-induction}}
\end{equation*}
This is sufficient to apply the induction hypothesis to each \(x\)-restricted
strategy, since the restricted strategies have dimension \(m\), and
\((m+1)d\ge md\).

After the restricted measurements have been improved to projective
submeasurements, the proof pastes them into a measurement in dimension \(m+1\).
The pasting theorem invoked at this point has its own size hypothesis.  In the
notation of the successor step, it requires
\begin{equation*}
  k\ge 400md.
  \tag{\path{thm:ld-pasting-in-induction-section}}
\end{equation*}
This condition is not a consequence of \(k\ge (m+1)d\).  For instance, when
\(m=1\) and \(d>0\), the latter allows \(k=2d\), whereas the pasting theorem
requires \(k\ge 400d\).  Thus the argument as written does not justify the
successor step throughout the interval in which \(k\ge (m+1)d\) but
\(k<400md\).

Equivalently, the missing implication is
\[
  k\ge (m+1)d
  \quad\Longrightarrow\quad
  k\ge 400md,
\]
which is false for the relevant range of parameters.  The issue is therefore a
missing side condition, not a notational convention or a peculiarity of the
formal language.

\section{The corrected formal interface}

The repair made in the checked formal statements is to state explicitly the
hypothesis used by the proof.  The source-labelled blueprint theorem is now
stated with the corrected bound \(k\ge 400md\).  In the successor step from
\(m\) to \(m+1\), one assumes \(k\ge 400(m+1)d\).  This immediately supplies the
pasting hypothesis \(k\ge 400md\) needed for the restricted dimension.

The current formal interface to the main formal theorem is adjusted in the same
way: its hypothesis on \(k\) is \(k\ge 400md\), rather than \(k\ge md\).  It
also requires \(k>0\).  This positivity is not a bridge or
measurement-construction hypothesis; it is a scalar boundary needed for the
Step~8 cascade estimates, which use \(1\le k\) to absorb lower-order terms into
the final envelope.  The printed theorem should therefore be read as missing
both the factor-\(400\) strengthening and the nonzero sampling-parameter
boundary for the present proof route.  The factor-\(400\) strengthening is now
treated as a confirmed statement correction, not as a proof obligation for the
interval \(md\le k<400md\).  The degenerate case \(k=0\) when \(d=0\) is handled
as the separate statement correction documented in
\path{docs/paper-gaps/issue-422-main-formal-zero-k-boundary.tex}.  A trivial
construction is used only when the final error parameter is already at least
\(1\), in which case the consistency conclusion is saturated.
\footnote{After the 2026-05-22 statement correction, the source-labelled
blueprint theorem for main induction links to the corrected Lean statement
\leanid{MIPStarRE.LDT.MainInductionStep.mainInduction_sourceStatement}.  The
main formal source theorem links to
\leanid{MIPStarRE.LDT.Test.mainFormal_sourceStatement}.  The final source
theorem routes through the named
wrapper \leanid{MIPStarRE.LDT.Test.mainFormal_sourceObligation}; its
saturated-error branch is proved, and its non-vacuous branch is
\leanid{MIPStarRE.LDT.Test.mainFormal_sourceSmallErrorObligation}.  The
small-error branch is reduced to the checked role-register scalar absorption
theorem under the corrected nonzero sampling hypothesis
\leanid{MIPStarRE.LDT.Test.mainFormal_sourceConclusion_ofRoleRegisterScalarBoundary};
The scalar lemma \leanid{MIPStarRE.LDT.Test.mainFormalError_zero_k} records
that the displayed final-theorem error is exactly zero at \(k=0\).
The Lean theorem \leanid{MIPStarRE.LDT.Test.mainFormal} assumes
\(400\,md\le k\) and \(0<k\); the pasting theorem is
\leanid{MIPStarRE.LDT.Pasting.Bernoulli.ldPastingNontrivial}, with
the corresponding large-\(k\) hypothesis.  The final assembly in
\path{MIPStarRE/LDT/Test/MainTheorem/MainFormal.lean} no longer depends on an
unfinished corrected large-\(k\) Section~6 successor construction.  The
zero-sampling boundary has likewise been removed from the source statement by
the explicit hypothesis \(0<k\).}

\section{Non-vacuity of the discarded printed interval}

The interval \(md\le k<400md\) is not eliminated by the ``large-error'' branch
of the formal proof.  The complementary case
\[
  m^2\left(\nu+\exp\!\left(-\frac{k}{80000m^2}\right)\right) < 1.
\]
This inequality can hold inside \(md\le k<400md\).  For example, take
\(m=2\), \(k=2d\), and choose \(d\) large enough that
\[
  4\exp\!\left(-\frac{d}{160000}\right)<\frac12.
\]
With \(\varepsilon=\delta=\gamma=0\), the remaining contribution to \(\nu\) is
controlled by \((d/q)^{1/1024}\).  Taking the field size \(q\) sufficiently
large makes
\[
  4\cdot 1000\cdot (2d)^2\cdot 2^2\cdot (d/q)^{1/1024}<\frac12.
\]
Thus the formal small-error branch is not vacuous; it requires a mathematical
argument for the source interval, or a corrected statement restricting the
theorem to the large-\(k\) range used by the pasting route.  It should not be
replaced by a hidden assumption on the paper-facing theorem.  The project now
takes the second option: the theorem statement is corrected to the large-\(k\)
range.

The same phenomenon occurs in the final theorem.  The wrapper
\leanid{MIPStarRE.LDT.Test.mainFormal_sourceObligation} proves the branch
\(\nu\ge 1\) by the trivial two-space consistency bound, but the source theorem
also has a complementary branch in which
\[
  100000 k^2m^4\left(\varepsilon^{1/40000}
    +(d/q)^{1/40000}
    +\exp\!\left(-\frac{k}{2560000m^2}\right)\right)<1.
\]
Taking again \(m=2\), \(k=2d\), \(d\) sufficiently large, and then \(q\)
sufficiently large, with \(\varepsilon=0\), gives examples in the printed
interval \(md\le k<400md\) where this final error is below \(1\).  Hence the
factor-\(400\) correction is also necessary for the final theorem route; after
this correction, the zero-sampling boundary is handled by the separate
nonzero-\(k\) correction.

\section{Conclusion}

The verdict is that
\href{https://github.com/LionSR/MIPStarRE/issues/906}{issue \#906} records a
genuine theorem-level side-condition gap in the stated proof.  The hypothesis
\(k\ge md\), or in the successor step \(k\ge (m+1)d\), does not imply the
large-\(k\) hypothesis required by the pasting theorem.  The current blueprint
therefore records the confirmed correction directly in the source-labelled
main-induction statement.  The final theorem route records the same large-\(k\)
correction; the zero-sampling obstruction is handled by the separate nonzero
sampling correction recorded in
\texttt{docs/paper-gaps/issue-422-main-formal-zero-k-boundary.tex}.

This correction does not assert that the mathematical conclusion is false for
\(md\le k<400md\).  It says that the cited proof route through the stated
pasting theorem does not establish that range.  The formalization therefore
uses the large-\(k\) theorem that the proof actually supports.  The separate
\(k=0\) boundary allowed when \(d=0\) is excluded from the corrected final
theorem statement by the hypothesis \(0<k\).

\bibliographystyle{alpha}
\bibliography{references}

\end{document}
