\documentclass[11pt]{article}

\usepackage{amsmath,amssymb}
\usepackage{xurl}
\usepackage[hidelinks]{hyperref}
\setlength{\emergencystretch}{2em}

\input{docs/paper-gaps/command}

\newcommand{\bx}{\mathbf{x}}
\newcommand{\by}{\mathbf{y}}
\newcommand{\bu}{\mathbf{u}}
\newcommand{\bv}{\mathbf{v}}
\newcommand{\ABAB}{\textit{ABAB}}
\newcommand{\ABA}{\textit{ABA}}
\newcommand{\BAB}{\textit{BAB}}
\newcommand{\closenessOfIP}{\text{closenessOfIP}}

\title{Issue 760: The Ten-Step Scalar Chain in the Processed-$G$
Commutativity Lemma}
\author{}
\date{\today}

\begin{document}
\maketitle

\section{The assertion}

This note examines the evaluated-slice commutativity lemma for the
processed $G$ measurements\footnote{The lemma carries the label
\texttt{lem:comm-data-processed-g} in
\path{references/ldt-paper/commutativity-G.tex}, lines~16--47, and is
tracked in
\href{https://github.com/LionSR/MIPStarRE/issues/760}{GitHub issue
\#760}.}
in \cite{Ji2020LowIndividualDegree}. The lemma states that, under the
three hypotheses of consistency with $A$, strong self-consistency, and
boundedness, the $G$ measurements approximately commute after
evaluation for distinct point pairs. The conclusion is
\begin{equation}\label{eq:processed-conclusion}
  \mathbb{E}_{\bu,\bv,\bx,\by} \sum_{a,b}
    \|(G^{\bx}_{[g(\bu)=a]} G^{\by}_{[h(\bv)=b]}
      - G^{\by}_{[h(\bv)=b]} G^{\bx}_{[g(\bu)=a]})
    \otimes I | \psi\rangle\|^{2}
  \leq
  \nu ,\qquad
  \nu = 48m (\sqrt{\gamma} + \sqrt{\zeta}).
\end{equation}

\section{The ten-step chain}

The paper's proof expands the commutator square and isolates the
$\ABAB$ term. The path from $\mathbb{E}[\sum \ABAB]$ to
$\mathbb{E}[\sum \ABA]$ passes through ten approximation steps:
\begin{enumerate}
  \item Apply $\closenessOfIP$ with $A = G^{\bu,\bx}_a \otimes I$ and
    $B = I \otimes A^{\bu,\bx}_a$, at cost $2\sqrt{\zeta}$.
  \item Swap $A^{\bv,\by}_b$ onto the right register, at cost
    $\sqrt{\zeta}$.\footnote{Justified by the auxiliary claim
    \texttt{clm:g-comm-stability} in the cited paper.}
  \item Insert Bob's second measurement via $\closenessOfIP$, at cost
    $2\sqrt{\zeta}$.
  \item Apply point commutativity, at cost
    $6\sqrt{\gamma(m+1)}$.\footnote{The point-commutativity theorem,
    labelled \texttt{thm:commutativity-points}.}
  \item Remove the right-register $G^{\bx}$ total, at cost
    $\sqrt{\zeta} + 6\sqrt{\gamma(m+1)}$.\footnote{Justified by
    \texttt{clm:g-comm-stability2}.}
  \item Reverse the $\closenessOfIP$ insertion of $A$ on the left
    register, at cost $4\sqrt{\zeta}$ (steps~6--7 of the paper).
  \item Post-process $G$ measurement outcomes, at cost
    $\sqrt{\zeta}$.\footnote{Justified by an auxiliary fact derived
    in the formalization.}
  \item Reverse the second-coordinate post-processing, at cost
    $\sqrt{\zeta}$.
\end{enumerate}
The individual error terms sum to
$12\sqrt{\zeta} + 12\sqrt{\gamma(m+1)}$.
Multiplying by~$2$ (from the commutator-square expansion) and
simplifying $12\sqrt{m+1} \leq 24m$ gives
$\nu = 48m(\sqrt{\gamma}+\sqrt{\zeta})$.

\section{The Lean formalization}

The formal lemma replicates the same ten-step
chain.\footnote{The declaration is
\path{MIPStarRE.LDT.Commutativity.commDataProcessedG}, implemented in
\path{MIPStarRE/LDT/Commutativity/ScalarApproximation/ProcessedG.lean},
lines~1972--2004; the error parameter
\texttt{commDataProcessedGError}, defined in
\path{MIPStarRE/LDT/Commutativity/Scaffold/Core.lean}, evaluates to
$48\,m\,(\gamma^{1/2} + \zeta^{1/2})$.}
Each paper step is recorded as a named phase block, and the final
assembly adds them with the factor~$2$ from the commutator-square
expansion. The total matches the paper exactly.

The one substep that deserves explicit mention is the transition from
the $\BAB$ term to the $\ABA$ term. In the paper this is justified by
the projectivity of~$G$, which makes
$\mathbb{E}[\sum G^{\bx}_{[g(\bu)=a]} G^{\by}_{[h(\bv)=b]}]
= \mathbb{E}[\sum G^{\by}_{[h(\bv)=b]} G^{\bx}_{[g(\bu)=a]}]$,
an exact equality. The formal proof uses the corresponding swap
lemma\footnote{The lemma
\texttt{evaluatedSliceCommutation\_avg\_swap\_terms} in
\path{MIPStarRE/LDT/Commutativity/EvaluatedSliceCommutation/Averages.lean},
line~217.}
which proves
$\operatorname{avgOver}_{\mathcal{D}}(\operatorname{avgBAB})
= \operatorname{avgOver}_{\mathcal{D}}(\operatorname{avgABA})$
as an \emph{equality} (not an approximation), exactly matching the
paper's step.

\section{Conclusion}

\noindent\textbf{Verdict:} no mathematical divergence. The Lean
ten-step chain follows the paper's proof step-by-step, uses the same
auxiliary lemmas (closeness of inner products, point commutativity,
and $G$-commutativity stability), and achieves the same total error
bound $48m(\sqrt{\gamma}+\sqrt{\zeta})$. The swap identity
$\operatorname{avgBAB} = \operatorname{avgABA}$ is an exact equality in
both the paper and the formalization. This note therefore documents a
successful alignment, not a gap.

\bibliographystyle{alpha}
\bibliography{docs/paper-gaps/references}

\end{document}