\documentclass{article}

\usepackage{amsmath,amssymb}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\setlength{\emergencystretch}{2em}

\input{docs/paper-gaps/command}

\title{Issue 1622: The Degree-Zero Branch of Low-Degree Pasting}
\author{}
\date{2026-05-14}

\begin{document}
\maketitle

\section{At a glance}

\begin{itemize}
  \item \textbf{Difficulty: medium.}  The missing case is not a new
  high-dimensional construction, but the positive-degree scalar absorption used
  in the present proof disappears when \(d=0\).
  \item \textbf{Estimated weight:} one separate branch theorem, probably
  \textbf{100--300 lines} of project-local proof, depending on how much of the
  line-test and slice-consistency API can be reused directly.
  \item \textbf{Mathlib/project split:} about \textbf{10\% Mathlib} and
  \textbf{90\% project-local}.  Mathlib should supply only elementary finite
  sums and scalar inequalities.
  \item \textbf{Key inputs:} degree-zero polynomial evaluation, the
  slice-consistency hypotheses in low-degree pasting, and the existing
  point-consistency interfaces for pasted measurements.
\end{itemize}

\section{Key theorem forms}

Let \(S\) be an
\((\varepsilon,\delta,\gamma)\)-good symmetric strategy for the
\((m+1,q,d)\) low individual degree test.  For each \(x\in\F_q\), let
\[
  G^x\in\polysub{m}{q}{d}
\]
be the projective submeasurement supplied on the \(x\)-slice, and assume the
completeness, consistency, strong self-consistency, and boundedness hypotheses
appearing in the source theorem.

The source theorem asserts that, if \(k\ge 400md\), then there is a pasted
measurement
\[
  H\in\polymeas{m+1}{q}{d}
\]
whose point-consistency error is
\[
  \sigma=\kappa\left(1+\frac{1}{100m}\right)+2\nu+
  \exp\left(-\frac{k}{80000m^2}\right),
\]
where
\[
  \nu=100k^2m\left(\varepsilon^{1/32}+\delta^{1/32}
    +\gamma^{1/32}+\zeta^{1/32}+(d/q)^{1/32}\right).
\]
No hypothesis \(0<d\) appears in this theorem.

The present positive-degree construction proves the same conclusion in the
nontrivial regime
\[
  \gamma\le 1,\qquad \zeta\le 1,\qquad d\le q,\qquad 0<d,\qquad 1\le k.
\]
The open branch should prove the source conclusion under the complementary
degree-zero hypotheses
\[
  d=0,\qquad 1\le k,
\]
without adding \(0<d\) or any bridge, residual, repair, producer, or package
hypothesis to the source-facing theorem.%
\footnote{The source-facing Lean theorem is
\(\leanid{MIPStarRE.LDT.Pasting.ldPasting}\).  The positive-degree theorem is
\(\leanid{MIPStarRE.LDT.Pasting.ldPastingNontrivial}\).  The open branch is
\(\leanid{MIPStarRE.LDT.Pasting.ldPastingDegreeZeroBranch}\) in
\doclink{MIPStarRE/LDT/Pasting/Bernoulli/Final.lean}.  The repair is tracked by
\ghissue{1622} and currently documented in \ghpr{1633}.}

\section{The source assertion}

This note concerns the low-degree pasting theorem in
\cite{Ji2020LowIndividualDegree}.%
\footnote{The TeX source used here is
\path{references/ldt-paper/ld-pasting.tex}, lines~12--55.  The theorem is
labelled \path{thm:ld-pasting}.}
After stating the theorem, the paper says that the proof may assume
\(\varepsilon,\delta,\gamma,\zeta,d/q\le 1\), since the desired bound is
trivial if one of these quantities is at least \(1\).  This is a reduction to
the small-error regime.  It is not a hypothesis \(0<d\), and it does not by
itself dispose of the case \(d=0\).

The point is visible in the error term itself.  When \(d=0\), the displayed
contribution \((d/q)^{1/32}\) is zero.  Thus any proof step that pays a positive
loss of order \(1/q\) or \(k^2/q\) cannot be justified merely by appealing to
the term \((d/q)^{1/32}\).

\section{Why the positive-degree proof does not specialize}

The current nontrivial proof follows the sampled distinct-tuple construction in
the paper.  In the estimates corresponding to the \(H_B\)-consistency and
overall-outcome steps, the argument passes between independently sampled
heights and distinct sampled heights.  This passage introduces a distinctness
loss of order \(k^2/q\).

For \(0<d\), this loss is absorbed into the displayed error term by the scalar
chain
\[
  \frac{1}{q}\le \frac{d}{q}\le \left(\frac{d}{q}\right)^{1/32},
\]
in the small-error regime.  The first inequality is exactly where the
positive-degree hypothesis enters.  When \(d=0\), the right-hand side is zero,
so the same scalar argument cannot close the estimate.

This is not evidence that the paper theorem should acquire the hypothesis
\(0<d\).  Rather, it shows that the formal proof has separated two branches:
the existing positive-degree argument and the remaining degree-zero argument.
In the degree-zero branch, one expects to use that every degree-zero polynomial
is constant, and then obtain point consistency from the line-test and
slice-consistency hypotheses without paying a distinct-tuple loss that must be
absorbed by \(d/q\).

\section{Comparison with the blueprint and formalization}

The formal development now keeps the unrestricted source-facing theorem form
visible.  Its proof dispatches the large-\(\gamma\), large-\(\zeta\),
large-\(d/q\), \(k=0\), and positive-degree nontrivial cases.  The only
remaining branch is the degree-zero case described above.  The branch is
therefore recorded as a direct proof obligation, not as an additional public
assumption of the theorem.

This is the intended paper-realignment boundary.  The restricted
positive-degree theorem remains useful proof content, but it should be cited
only as a nontrivial-regime construction theorem.  It should not replace the
source theorem in the blueprint, because its public hypotheses are stronger
than the cited statement.

\section{Conclusion}

There is no current justification for adding \(0<d\) to the paper-facing
low-degree pasting theorem.  The theorem-level statement should remain the
unrestricted statement of the source.  The missing work is the separate
degree-zero branch: prove the pasted measurement and point-consistency estimate
from \(d=0\), \(1\le k\), and the source hypotheses, or keep that branch as a
tracked \Lean{} proof obligation until the argument is supplied.

\bibliographystyle{alpha}
\bibliography{docs/paper-gaps/references}

\end{document}
