\documentclass{article}

\usepackage{amsmath,amssymb}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\setlength{\emergencystretch}{2em}

\input{docs/paper-gaps/command}

\title{Foundation-layer formalization design:\\
finite fields, distributions, and a zero family}
\author{}
\date{\today}

\begin{document}
\maketitle

\section{The setting}

The low individual degree test of \cite{Ji2020LowIndividualDegree}
works over a finite field $\F_q$, where $q = p^t$ is a prime power.
The field structure enters the argument in two essential ways:
through the polynomial calculus that supports the Schwartz--Zippel
lemma, and through the additive characters $\omega^{\tr[\,\cdot\,]}$
used in the Fourier-analytic estimates. In addition, the proofs make
constant use of expectations over uniform distributions on $\F_q^m$,
on lines, and on sampled question pairs. These three ingredients---
the field, the distributions, and the conventions used to manipulate
them---constitute what we shall call the \emph{foundation layer} of
the formalization.\footnote{The choices discussed here were collected
in \ghissue{458}.}

In adapting the paper to a formal proof assistant we are obliged to
make explicit several conventions that the prose leaves implicit:
how to record the prime-power hypothesis on $q$, how to represent
finitely supported probability distributions, and what to do with
operator families that the paper never names but which arise as
algebraic zero objects in the formal manipulations. We record those
conventions here and verify that none of them silently change a
hypothesis or conclusion of the cited argument.

\section{The field parameter $q$}

We are given that $q = p^t$ is a prime power; this is stated at the
beginning of the preliminaries\footnote{See the source preamble in
\path{references/ldt-paper/preliminaries.tex}, lines~17--19 and
89--93.} of \cite{Ji2020LowIndividualDegree}. In the formal
development we separate two roles played by this hypothesis. The
\emph{assertion} that $q$ is a prime power is recorded as a bare
existential
\[
  \exists\, p, n,\quad p\text{ prime},\ n \ge 1,\ q = p^n,
\]
attached to a numerical value $q \in \N$ in a parameter
record.\footnote{The carrier and the prime-power witness live in the
structure \leanid{Parameters} (\path{MIPStarRE/LDT/Basic/ParametersBase.lean},
line~36), with field \leanid{hqPrimePower} of the displayed
existential type.}  The \emph{use} of a finite field of order $q$ is
delegated to a separate typeclass which bundles a field $K$, a
\leanid{Fintype} instance, and a coding bijection $K \simeq
\leanid{Fin}\,q$.\footnote{This is the typeclass
\leanid{FieldModel params.q} in \path{ParametersBase.lean}, line~224;
its canonical instance is constructed from the prime-power witness
via \leanid{PrimePowerFieldSpec.toFieldModel}, which produces the
Mathlib finite field \leanid{GaloisField}\,$p$\,$n$.}

Arithmetic on scalars is therefore carried out inside the field $K$,
while combinatorial sums, expectations, and indexing pass through
$\leanid{Fin}\,q$ via the explicit decoding/encoding maps. The
prime-power assertion is needed only to derive $q \ge 2$, the
non-vanishing of $|\F_q|$, and the existence of an honest field of
order $q$; these are exactly the properties used in the paper. The
field $\F_q$ of the cited argument and the field inhabited by the
typeclass are the same object up to canonical isomorphism. This is
a matter of formalization design and not of mathematics: no
hypothesis or conclusion is altered.

\section{Probability distributions}

The paper writes its averages in the standard informal style: the
expectation $\E_{\bx \in \F_q^m}$ over a uniform point, the
expectation over a uniformly random line, and so on. In the formal
development we make these explicit by representing a distribution as
a finite support together with a non-negative real weight on each
point, subject to an \leanid{IsProbability} predicate that the total
weight equals $1$.\footnote{The type \leanid{Distribution} is defined
in \path{MIPStarRE/LDT/Basic/Distribution.lean} at line~17, with
\leanid{avgOver} the corresponding average over the explicit support.}
The uniform distribution on a nonempty finite type is then a derived
case, and every expectation in the paper becomes a finite sum over an
explicit support.

This is a self-contained reimplementation of a fragment of measure
theory, and is in principle redundant with the probability layer of
Mathlib; we adopt the lighter-weight type because every distribution
we encounter is finite and explicitly supported. It faithfully
represents each of the paper's expectations, and no mathematical
statement depends on the choice.

\section{The zero family}

The full-slice commutation transport requires a neutral element in
the family of operator-valued measurements ordered by the
state-dependent distance relation. We introduce for this purpose a
measurement family in which every outcome and the total are equal to
the zero operator.\footnote{The declaration
\leanid{zeroFullSliceOpFamily} appears in
\path{MIPStarRE/LDT/Commutativity/Transport/FullSlice.lean},
line~26.}  Its safety is recorded by a single lemma\footnote{The
lemma \leanid{fullSliceProductLeft\_to\_zero\_le\_one} in the same
file, line~216.} which bounds the state-dependent distance between
this zero family and the actual full-slice product by $1$ on a
normalized state, an estimate that follows directly from the
definitions.

The cited argument never names such a family. It instead writes out
the corresponding inequalities directly, term by term. The zero
family is therefore a packaging convenience for those same
inequalities; it asserts nothing that the paper would contradict.

\section{Conclusion}

There is no mathematical discrepancy. The formalization records the
prime-power hypothesis on $q$ as an existential proof and accesses
the corresponding finite field through a typeclass; it represents the
paper's expectations as finite weighted sums; and it introduces a
zero measurement family purely as a packaging device for elementary
inequalities already present in the paper. Each choice is a
formalization decision, and each preserves the mathematics of the
cited argument exactly.

\bibliographystyle{alpha}
\bibliography{docs/paper-gaps/references}

\end{document}