\documentclass{article}

\usepackage{amsmath,amssymb}
\usepackage{xurl}
\usepackage[hidelinks]{hyperref}
\setlength{\emergencystretch}{2em}

\input{command}

\title{The Restricted Interface of the Main Formal Soundness Theorem}
\author{}
\date{2026-05-01}

\begin{document}
\maketitle

\section{At a glance}

This note is now historical.  As of 2026-05-23, the interface restriction
recorded below has been removed from the corrected source theorem.  The Lean declaration
\leanid{MIPStarRE.LDT.Test.mainFormal\_sourceStatement} is stated for a
general two-space projective strategy \leanid{MIPStarRE.LDT.ProjStrat} on
\(\mathcal H_{\mathrm A}\otimes\mathcal H_{\mathrm B}\).  The heterogeneous
role-register construction and the subsequent unsymmetrization,
orthonormalization, completion, line-169 transport, final point-evaluation
triangle, and scalar absorption are checked under the corrected assumptions
\(k\ge 400md\) and \(0<k\).  The old same-space restriction is no longer a
current obstruction.

The same-space theorem \leanid{MIPStarRE.LDT.Test.mainFormal} remains as a
useful Lean interface, but it is no longer the source theorem.  The remaining
differences from the literal printed statement are the documented large-\(k\)
correction and the nonzero sampling boundary, not the old same-space
role-register restriction.

\begin{itemize}
  \item \textbf{Difficulty: resolved.}  The former discrepancy was an interface
  restriction: the earlier checked theorem used a same-space, swap-compatible
  strategy object, while the paper starts from an arbitrary two-space projective
  strategy and then symmetrizes it.
  \item \textbf{Estimated weight: completed source-boundary repair.}  The
  checked route now includes the heterogeneous role-register construction,
  unsymmetrization, two-sided orthonormalization and completion, line-169
  transport, point-evaluation triangle, and scalar absorption.
  \item \textbf{Mathlib/project split:} mostly project-local.  Mathlib supplies
  finite type, matrix-order, and tensor-placement infrastructure; the
  role-register and source-boundary constructions are project-specific.
  \item \textbf{Key Mathlib inputs:} finite direct sums or tagged products,
  matrix block embeddings, tensor-placement identities, state-dependent
  distance estimates, and order monotonicity for expectations.  The
  project-local inputs are \leanid{MIPStarRE.LDT.ProjStrat},
  \leanid{MIPStarRE.LDT.SameSpaceProjStrat}, the heterogeneous role-register
  construction, and the Section~5 projectivization route.  Tracked in
  \ghissue{930}.
\end{itemize}

\section{Key theorem forms}

The comparison separates the source theorem from the current formal interface.
\begin{enumerate}
  \item \textbf{Printed source form.}  The paper's main theorem starts from a
  general projective strategy on
  \(\mathcal H_{\mathrm A}\otimes\mathcal H_{\mathrm B}\), with no assumption
  that the two local spaces coincide and no assumption that the original state
  is already symmetric.  The Lean declaration
  \leanid{MIPStarRE.LDT.Test.mainFormal_sourceStatement} records this source
  statement and factors the remaining source-boundary work through the named
  wrapper \leanid{MIPStarRE.LDT.Test.mainFormal_sourceConclusion}.  This wrapper
  proves the saturated-error branch and leaves the non-vacuous branch as
  \leanid{MIPStarRE.LDT.Test.mainFormal_sourceSmallErrorConclusion}.
  \item \textbf{Current formal-interface form.}  The Lean theorem
  \leanid{MIPStarRE.LDT.Test.mainFormal} is stated for the same-space strategy
  interface \leanid{MIPStarRE.LDT.SameSpaceProjStrat}.  The source-labelled
  blueprint theorem remains separate from the current-interface entry.
  \item \textbf{Expected adapter form.}  A future theorem should construct the
  role-register symmetrized strategy directly from the two-space container
  \leanid{MIPStarRE.LDT.ProjStrat}, or prove that the paper's general strategy
  reduces to the same-space formal interface without changing the source
  hypotheses.
\end{enumerate}

\section{The assertion}

The main formal soundness theorem in \cite[Section~\emph{The test}]{Ji2020LowIndividualDegree}
starts from a general projective strategy for the $(m,q,d)$ low individual degree
test. In the paper, such a strategy consists of a bipartite state on
$\mathcal H_{\mathrm A}\otimes\mathcal H_{\mathrm B}$ and separate projective
measurement families for the two provers. The two local Hilbert spaces are not
assumed to be the same, and the starting state is not assumed to be symmetric.
The test definition takes $m$ and $d$ to be non-negative integers, and the
main theorem as printed does not impose a separate hypothesis $d>0$.\footnote{The
earlier formal interface also carried such a positive-degree hypothesis.  This
has now been removed from \leanid{MIPStarRE.LDT.Test.mainFormal}; the remaining
restriction recorded in this note is the same-space strategy interface.  This
note is part of the retrospective audit in \ghissue{930}. The paper passages are
\path{references/ldt-paper/test_definition.tex}, lines~10--14, 98--115, and
180--202, together with the reduction in
\path{references/ldt-paper/inductive_step.tex}, lines~26--66. The previously
documented large-$k$ correction is separate; see
\path{docs/paper-gaps/issue-906-main-formal-k-bound.tex}.}

After stating the theorem for this general strategy, the paper symmetrizes it by
adding a two-dimensional role register on each side. In the proof, the paper
first treats the case in which the two local Hilbert spaces have the same
dimension and says that the construction extends to different dimensions. Even
in that simplified proof setting, however, the original state is not assumed to
be swap-invariant. The symmetrized state is a sum of two role sectors: one sector
carries the original state, and the other sector carries the state with the
tensor factors interchanged. The purpose of this step is precisely to pass from
a not-necessarily-symmetric general strategy to a symmetric strategy to which the
main induction theorem can be applied.

\section{The formal interface}

The present formal development contains a paper-faithful two-space container
for general projective strategies, \leanid{MIPStarRE.LDT.ProjStrat}, and the
corrected source theorem
\leanid{MIPStarRE.LDT.Test.mainFormal\_sourceStatement} is stated for that
container.  The same-space theorem \leanid{MIPStarRE.LDT.Test.mainFormal}
remains as a separate auxiliary interface for the symmetric carrier, but it is
not the theorem advertised as the source statement.\footnote{The two-space
strategy container is \leanid{MIPStarRE.LDT.ProjStrat}; the same-space special
case is \leanid{MIPStarRE.LDT.SameSpaceProjStrat}.  Pull request \ghpr{958}
closed \ghissue{560} by making \leanid{ProjStrat} two-space.  The later
source-boundary repair generalized the final theorem route through the
heterogeneous role-register construction.}

The blueprint records the same interface boundary. It describes the paper's
general projective strategy in the source theorem
\texttt{thm:main-formal}, links that entry to the source-faithful Lean
statement \leanid{MIPStarRE.LDT.Test.mainFormal_sourceStatement}, and records
the current same-space formal interface as a separate Lean-only entry,
\texttt{thm:main-formal-current-interface}.  This keeps the source-labelled
statement in the printed paper form while making the formal restriction
explicit.\footnote{See
\path{blueprint/src/chapter/ch02_test.tex}, lines~35--43 for the strategy split
and the formal soundness target section for the source theorem and the separate
current-interface entry.}

Thus the former same-space interface restriction is no longer a current
obstruction to the corrected source theorem.  A general strategy on
\(\mathcal H_{\mathrm A}\otimes\mathcal H_{\mathrm B}\) with different local
spaces, or with a nonsymmetric starting state, is now an input to
\leanid{MIPStarRE.LDT.Test.mainFormal\_sourceStatement}.  The former
positive-degree restriction is also no longer present in the public Lean
statement.

\section{Conclusion}

The discrepancy recorded in this note has been resolved.  The corrected source
theorem starts from the paper's general two-space projective strategy, and the
heterogeneous role-register reduction is checked.  This note remains in the
paper-gap directory as a historical record of the former same-space
restriction.

\bibliographystyle{alpha}
\bibliography{references}

\end{document}
