\documentclass[11pt]{article}

\usepackage{amsmath,amssymb}
\usepackage{xurl}
\usepackage[hidelinks]{hyperref}
\setlength{\emergencystretch}{2em}

\input{command}

\title{Issue 1228: The SVD Step in Orthonormalization}
\author{}
\date{2026-05-05}

\begin{document}
\maketitle

\section{At a glance}

\begin{itemize}
  \item \textbf{Difficulty: medium.}  The paper's SVD step is finite-dimensional
  linear algebra, and the current project already has the main positive-Gram
  construction.  A reusable Mathlib-quality rectangular SVD theorem would be
  harder.
  \item \textbf{Estimated weight:} about \textbf{3--6 theorem interfaces} and
  \textbf{300--700 lines} to finish or reuse the local route; a fully general
  rectangular complex SVD/polar theorem suitable for upstreaming would likely be
  \textbf{800--1500 lines}.
  \item \textbf{Mathlib/project split:} about \textbf{65\% Mathlib} and
  \textbf{35\% project-local} for the present route.  Mathlib supplies spectral
  theory, adjoints, orthonormal bases, and $\sqrt{\,\cdot\,}$; the project supplies
  the rectangular $X,\widehat X,P$ packaging and paper-specific estimates.
  \item \textbf{Key Mathlib inputs:} finite-dimensional inner-product spaces,
  matrix adjoints, Hermitian eigenvectors/eigenvalues, positive semidefinite
  matrices, and continuous-functional-calculus square roots.%
  \footnote{Representative APIs include \leanid{Orthonormal},
  \leanid{Matrix.IsHermitian.eigenvectorBasis},
  \leanid{Matrix.IsHermitian.eigenvalues}, \leanid{CFC.sqrt}, and
  \leanid{CFC.sqrt\_unique}.}
\end{itemize}

\section{The source step}

The SVD appears in the orthonormalization proof of
\cite{Ji2020LowIndividualDegree}.%
\footnote{The SVD passage is in
\path{references/ldt-paper/orthonormalization.tex}, lines~774--845.}
After rounding and rank reduction, the paper has projectors $Q_a$ with
$Q=\sum_aQ_a$ and $\sum_a\operatorname{rank}(Q_a)\le d$.  It chooses vectors
$\ket{v_{a,i}}$ spanning the ranges of the $Q_a$ and defines
\[
  X_a=\sum_i\ket{a,i}\bra{v_{a,i}},
  \qquad
  X=\sum_aX_a,
  \tag{\texttt{[blueprint] def:matrix-decomposition-Q}}
\]
with auxiliary projectors $T_a$.  The basic identities are
\[
  X_a=T_aX,
  \qquad
  Q_a=X_a^\dagger X_a=X^\dagger T_aX.
  \tag{\texttt{lem:xa-t},\ \texttt{lem:qa-restated}}
\]
Since the total rank is at most $d$, the matrix $X$ is $m\times d$ with $m\le d$.
The paper takes an SVD
\[
  X=U\Sigma_{m\times d}V^\dagger.
  \tag{\texttt{[blueprint] def:svd-of-X}}
\]

\section{What the SVD supplies}

The paper replaces the singular values of $X$ by $1$:
\[
  \widehat X=UI_{m\times d}V^\dagger,
  \qquad
  P_a=\widehat X^\dagger T_a\widehat X.
  \tag{\texttt{[blueprint] def:projective-P}}
\]
Only three consequences are used later.%
\footnote{The first consequence, \texttt{lem:X-hat-squared}, is proved in
\path{references/ldt-paper/orthonormalization.tex}, lines~984--1001.  The
second, \texttt{lem:X-times-X-hat}, is proved in lines~1005--1034, and the
third, \texttt{lem:squared-difference}, in lines~1036--1064.  Each proof uses
the auxiliary identities $XX^\dagger=U\Sigma_{m\times m}^2U^\dagger$ and
$X^\dagger X=Q$ from \texttt{lem:X-squared}, lines~862--896.}

\begin{enumerate}
  \item \textbf{Coisometry:} $\widehat X\widehat X^\dagger=I_{m\times m}$.  This
  makes $P=\{P_a\}$ projective.
  \item \textbf{Square-root coupling:} $X^\dagger\widehat X=\sqrt Q$, because
  $X^\dagger X=Q$ and the corresponding middle SVD factor is positive.
  \item \textbf{Squared difference:}
  \[
    (X-\widehat X)(X-\widehat X)^\dagger
    \le (XX^\dagger-I_{m\times m})^2.
  \]
  This is the scalar inequality $(\sigma-1)^2\le(\sigma^2-1)^2$ for
  $\sigma\ge0$, after multiplying by $(\sigma+1)^2\ge1$.
\end{enumerate}

These facts enter one Cauchy--Schwarz estimate and give
\[
  Q_a\ot I\approx_{30\zeta^{1/4}}P_a\ot I.
  \tag{\texttt{lem:P-Q-approx}}
\]
Together with $A_a\ot I\approx_{12\sqrt\zeta}Q_a\ot I$, this yields
$A_a\ot I\approx_{84\zeta^{1/4}}P_a\ot I$.%
\footnote{The $P$-versus-$Q$ estimate and final triangle step are in
\path{references/ldt-paper/orthonormalization.tex}, lines~1089--1192.}

\section{Key theorem forms to develop}

The formalization should isolate the following theorem forms.

\begin{enumerate}
  \item \textbf{Rectangular polar theorem.}  If $X$ is $m\times d$, $m\le d$,
  and $Q=X^\dagger X$, then there exists $\widehat X$ such that
  \[
    \widehat X\widehat X^\dagger=I_m,
    \qquad
    X^\dagger\widehat X=\sqrt Q.
  \]

  \item \textbf{SVD adapter.}  If $X=U\Sigma V^\dagger$ and
  $\widehat X=UI_{m\times d}V^\dagger$, then the two identities above follow
  from the unitary laws and positivity of the SVD middle factor.

  \item \textbf{Projectivity and approximation.}  For
  $P_a=\widehat X^\dagger T_a\widehat X$, the coisometry identity implies
  $P_aP_b=\mathbf 1_{a=b}P_a$, and the squared-difference estimate plus almost
  projectivity of $Q$ implies the $P$-versus-$Q$ bound.
\end{enumerate}

\section{Blueprint and formalization}

The blueprint follows the same sequence: matrix decomposition, SVD, definition of
$P$, then the three identities and the $P$-versus-$Q$ estimate.%
\footnote{See \path{blueprint/src/chapter/ch04_projective.tex}, lines~704--785
and 833--1153.}

The Lean development separates \textbf{packaging} from \textbf{linear algebra}.
The $X,\widehat X,P$ data package stores the identities needed downstream, while
wrappers keep the paper's objects visible and prove bookkeeping facts such as
$X^\dagger X=Q$.%
\footnote{The formal names are \leanid{svdOfX}, \leanid{QXPLayerData}, and
related constructors in
\doclink{MIPStarRE/LDT/MakingMeasurementsProjective/QXPLayer/Core.lean}.}
The substantive linear algebra is in two routes: explicit rectangular-SVD
adapters, and a positive-Gram construction that builds $\widehat X$ directly from
the positive spectral subspace of $Q$.%
\footnote{The relevant declarations include
\leanid{rectangularSvd\_xHat\_coisometry},
\leanid{rectangularSvd\_xHat\_mixed\_raw},
\leanid{rectangularSvd\_middle\_eq\_sqrt\_of\_square},
\leanid{exists\_xHat\_of\_rectangularSvd},
\leanid{exists\_xHat\_of\_positive\_gram\_spectrum}, and
\leanid{pQApprox\_ofRankReductionSigmaRangePositiveGram} in
\doclink{MIPStarRE/LDT/MakingMeasurementsProjective/QXPLayerIdentities.lean}.}
The version of Mathlib pinned here does not provide exactly the rectangular SVD
or polar theorem above, so the project-local positive-Gram route supplies it.%
\footnote{The local coisometry helper
\leanid{Matrix.exists\_mul\_conjTranspose\_eq\_one\_of\_card\_le} is in
\doclink{MIPStarRE/Quantum/FiniteHilbert.lean}.  Possible upstreaming is tracked
in \ghissue{1250}.}

\section{Conclusion}

There is \textbf{no mathematical discrepancy} in the paper's SVD step.  The SVD
is used only to construct $\widehat X$ with
$\widehat X\widehat X^\dagger=I$ and $X^\dagger\widehat X=\sqrt Q$, and to prove
the squared-difference estimate behind the $P$-versus-$Q$ bound.

The formalization preserves this mechanism.  It can use explicit rectangular-SVD
data when available, but the reliable project route is the positive-Gram
construction built from Mathlib spectral APIs.

\bibliographystyle{alpha}
\bibliography{references}

\end{document}
