\documentclass[11pt]{article}

\usepackage{amsmath,amssymb}
\usepackage{xurl}
\usepackage[hidelinks]{hyperref}
\setlength{\emergencystretch}{2em}

\input{command}

\title{Naimark dilation: projective-submeasurement form and the full bipartite assembly}
\author{}
\date{2026-05-08}

\begin{document}
\maketitle

\section{At a glance}

\begin{itemize}
  \item \textbf{Difficulty: discharged for the theorem used here.}  The
  one-measurement Naimark step, the restriction to the original outcomes, and
  the two-sided tensor-product trace identity are formalized in Lean in the
  projective-submeasurement form supplied by the helper lemma.
  \item \textbf{Estimated weight: completed in this branch.}  The final
  discharge consists of the local compression identity, the auxiliary-state
  construction, and the four-register trace calculation recorded in
  \leanid{OneMeasNaimarkData.twoSidedCorrelationPreservation} and
  \leanid{naimarkTensorProductCorrelation}.
  \item \textbf{Mathlib/project split:} the proof is mostly project-local
  matrix bookkeeping, with Mathlib supplying finite sums, matrix algebra,
  tensor-product positivity, and elementary field simplification.
  \item \textbf{Remaining note:} the paper's word ``measurement'' must be read
  in the projective-submeasurement sense supplied by the helper lemma.  The
  complete-measurement form on the original outcome type is false for arbitrary
  submeasurements because the residual mass is carried by the additional
  \(\bot\) outcome.
  \item \textbf{Key Mathlib inputs and mathematical inputs:}
  finite-dimensional matrix trace identities, Naimark's one-measurement
  compression identity, tensor-product states, and the register permutation
  used by the product-extension state.
\end{itemize}

\section{Key theorem forms}

The formalization isolates two related but distinct theorem forms.
\begin{enumerate}
  \item \textbf{Source theorem form: Naimark dilation
  (\texttt{thm:naimark}, displayed at
  \path{references/ldt-paper/orthonormalization.tex}, lines~36--115).}
  For every collection of bipartite
  submeasurements $\{A^x\}_{x\in Q_A}$, $\{B^y\}_{y\in Q_B}$ on a finite
  Hilbert space~$\mathcal H$, there is an enlarged Hilbert space $\widetilde
  {\mathcal H}\supseteq\mathcal H$, an isometry $V:\mathcal H\to\widetilde
  {\mathcal H}$, and projective submeasurements $\{\widetilde A^x\}$,
  $\{\widetilde B^y\}$ on $\widetilde{\mathcal H}\otimes\widetilde{\mathcal H}$
  with
  \[
    \langle\psi|A^x_a\otimes B^y_b|\psi\rangle
    =\langle V\psi|\widetilde A^x_a\otimes \widetilde B^y_b|V\psi\rangle.
    \tag{\texttt{thm:naimark}}
  \]
  This is the displayed paper statement at
  \path{references/ldt-paper/orthonormalization.tex}, lines~36--115, read
  through the helper lemma at lines~121--159.  The helper produces a
  projective submeasurement on the original outcomes; the residual mass is the
  additional $\bot$ outcome in the auxiliary register.
  \item \textbf{Adapter theorem form: per-question one-measurement
  Naimark.}  For each question $x$ and submeasurement $A^x$ there exists a
  one-measurement Naimark dilation on the enlarged space
  $\mathcal H\otimes(\C\oplus\C^{|\textsf{Outcome}|})$ that preserves all
  single-outcome expectations:
  \[
    \tau\bigl(\rho\,A^x_a\bigr)
    =\widetilde\tau\bigl(\widetilde\rho\,\widetilde A^x_{(a,\mathrm{some})}\bigr).
  \]
  This questionwise interface is also formalized; see the Lean structure
  \leanid{NaimarkStatement} and the Lean theorem
  \leanid{questionwiseNaimark}.  The derived declaration
  \leanid{OneMeasNaimarkData.toProjSubMeas} turns the checked
  \(\mathrm{Option}\)-outcome dilation into the projective submeasurement on
  the original outcomes.%
  \footnote{Defined at
  \doclink{MIPStarRE/LDT/MakingMeasurementsProjective/NaimarkOneMeas.lean}.}
  The source-facing theorem
  \leanid{naimarkTensorProductCorrelation} constructs the auxiliary spaces,
  auxiliary product state, dilated state, and projective submeasurements from
  the checked one-measurement theorem.  The four-register trace identity
  \leanid{OneMeasNaimarkData.twoSidedCorrelationPreservation} is proved.
  \item \textbf{Downstream theorem form.}  The downstream uses inside the LDT
  pipeline never call the bipartite tensor product of two Naimark dilations;
  they call the per-question single-outcome marginal-preservation conclusion at
  Alice or Bob separately, with the unmodified state on the unaffected side.
  This is supplied directly by \leanid{leftMarginalPreservation} and
  \leanid{rightMarginalPreservation}.
\end{enumerate}

\section{The source assertion}

We examine \cite{Ji2020LowIndividualDegree}, the Naimark dilation theorem
labelled \texttt{thm:naimark}.%
\footnote{Tracked alongside ledger~\ghissue{1379}.  The paper passages are
\path{references/ldt-paper/orthonormalization.tex}, lines~36--115 (the displayed
theorem statement), 121--159 (the helper lemma \texttt{lem:naimark-helper} and
its proof), 161--187 (the proof of \texttt{thm:naimark} that tensors the
per-question helpers), and 189--272 (the genuine non-preservation example
\texttt{ex:easy-but-long}).}

\medskip

\noindent\emph{Notation.}  We write $X\approx_\delta Y$ on the state $\ket\psi$
to mean the state-dependent operator distance
\(
  \langle\psi|(X-Y)^{\dagger}(X-Y)|\psi\rangle\le\delta,
\)
defined as in \cite{Ji2020LowIndividualDegree} at
\texttt{def:approx\_delta} (\path{references/ldt-paper/preliminaries.tex}, line~348).

\medskip

In the notation of the paper, the source assumes
\[
  \mathcal H=\text{a finite-dimensional Hilbert space},
  \quad \{A^x\}_{x\in Q_A},\,\{B^y\}_{y\in Q_B}\text{ submeasurements on }\mathcal H,
\]
and concludes the bipartite preservation identity above.  The proof proceeds
question by question via \texttt{lem:naimark-helper}.  That helper explicitly
produces a projective submeasurement indexed by the original outcomes.  This is
the mathematically necessary form for arbitrary submeasurements.  If one asks
instead for a complete projective measurement indexed by the original outcomes,
the assertion is false: take a one-outcome submeasurement $A_*=0$ on Alice's
space and a one-outcome measurement $B_*=I$ on Bob's space.  The original
correlation is zero.  But a one-outcome projective measurement on the enlarged
Alice and Bob spaces must have its unique effect equal to the identity, so any
normalized dilated state has correlation one.

The example
\texttt{ex:easy-but-long} demonstrates that the dilation does \emph{not}
preserve the state-dependent distance $\approx_\delta$ defined just above,
which is why downstream arguments in the LDT paper carry the dilation only as
far as the single-outcome marginals.

\section{Comparison with the formalization}

The blueprint and formal development together record the per-question
one-measurement dilations and the single-outcome marginal preservation, but
omit the global tensor-product assembly into one bipartite statement.  The
source-facing Lean statement has therefore been corrected to use projective
submeasurements on the original outcome types.  Equivalently, one could state a
completed version using projective measurements indexed by
\(\mathrm{Option}(\mathsf{Outcome})\), but that is not the outcome type used in
the source display.

The
formal development proves the adapter form
\[
  \forall x,a,\rho,\;
  \tau\bigl(\rho A^x_a\bigr)
  =\widetilde\tau\bigl(\widetilde\rho_x\,(\widetilde A^x)_{(a,\mathrm{some})}\bigr),
\]
where $\widetilde\rho_x$ is the one-measurement-lifted density at question $x$.
The corresponding statement for Bob is symmetric.  The bipartite identity of
the source theorem form is now proved by the four-register trace identity
\leanid{OneMeasNaimarkData.twoSidedCorrelationPreservation}.

The questionwise interface is still sufficient for downstream LDT use: every
consumer reduces to the per-side single-outcome marginal-preservation
conclusion, applied either to Alice's submeasurements with $B$ left untouched
or vice versa.  No consumer requires the simultaneous bipartite dilation, but
the source theorem is now available as an axiom-clean Lean theorem.

\section{What remains documented}

The former bipartite-assembly gap is closed.  The note remains because it
records a genuine correction to the source wording:
\begin{itemize}
  \item \textbf{Distance non-preservation.}  Example~\texttt{ex:easy-but-long}
  shows that the dilation does not preserve the state-dependent distance
  $\approx_\delta$ recalled in Section~3, so any
  bipartite statement formulated in terms of state-dependent distances would
  need to track an explicit error inflation that is not used downstream.
  \item \textbf{Projective-submeasurement conclusion.}  The helper lemma
  produces projectors on \(\mathrm{Option}(\mathcal A)\).  Restricting to the
  original outcomes gives a projective submeasurement.  It does not give a
  complete projective measurement on the original outcome type unless the
  original submeasurement was already complete.
  \item \textbf{Blueprint interpretation.}  The blueprint therefore states and
  links the theorem in the projective-submeasurement form, with this note
  recording why that is the faithful formal reading of the cited argument.
\end{itemize}

\section{Conclusion}

The Lean structure \leanid{NaimarkStatement} and theorem
\leanid{questionwiseNaimark} record the per-question one-measurement Naimark
data and the single-outcome marginal-preservation conclusions used by
downstream LDT lemmas.  The declaration
\leanid{OneMeasNaimarkData.toProjSubMeas} proves the local passage from the
completed \(\mathrm{Option}\)-outcome projective measurement to the projective
submeasurement on the original outcomes.  The source-facing tensor theorem
should be read in the projective-submeasurement form supplied by the paper's
helper lemma; the complete-measurement form on the original outcome type would
be false for submeasurements.  The simultaneous bipartite tensor-product
assembly is now proved by \leanid{naimarkTensorProductCorrelation}; no
Naimark-specific `sorryAx` remains.

\bibliographystyle{alpha}
\bibliography{references}

\end{document}
