\documentclass[11pt]{article}

\usepackage{amsmath,amssymb}
\usepackage{xurl}
\usepackage[hidelinks]{hyperref}
\setlength{\emergencystretch}{2em}

\input{command}

\title{The Nonnegativity Hypothesis in the Small-Overlaps Bound}
\author{}
\date{2026-04-30}

\newcommand{\Small}{\mathsf{Small}}

\begin{document}
\maketitle

\section{The assertion}

This note concerns the bound on the sum over small overlaps in the rank-reduction
step of the orthogonalization lemma,
\cite[Section~\emph{Orthogonalization lemma}]{Ji2020LowIndividualDegree}.
\footnote{The discrepancy recorded here was identified in
\href{https://github.com/LionSR/MIPStarRE/issues/938}{GitHub issue \#938}.
In the TeX source consulted here, the estimate occurs in
\path{references/ldt-paper/orthonormalization.tex}, lines 606--612.}
We use the notation of the cited source:
the overlaps $o_{a,i}$ are defined by
\[
  o_{a,i} = \langle \psi, (P_{v_{a,i}} \otimes I)\psi\rangle,
\]
where $\psi$ is the state and $P_{v_{a,i}}$ is the rank-one projection onto the
unit vector $v_{a,i}$ from the range of a projector. The total number of overlap
pairs is $r$, the set $\Small$ is the complement of the $d$ largest overlaps,
and $\zeta$ is the
self-consistency error parameter with $0\le \zeta\le 1/4$.

At this point the paper asserts the estimate
\begin{align}
  \sum_{(a,i)\in\Small} o_{a,i}
    &\le 4\sqrt{\zeta},
      \tag{\path{eq:small-overlaps}}
\end{align}
using the auxiliary bounds
\[
  |\Small| \le 2\sqrt\zeta \cdot r,
  \qquad
  \sum_{a,i} o_{a,i} \le 1+2\sqrt\zeta,
\]
together with the fact that every overlap in $\Small$ is at most every overlap
outside $\Small$. The proof of the auxiliary bounds uses the overlaps
themselves; they are manifestly non-negative because each is an expectation of a
positive operator against a state.

\section{The abstraction in Lean}

The formal development, following the blueprint, extracts the combinatorial
content of the estimate and proves it for an arbitrary real-valued function,
without assuming nonnegativity.
\footnote{The formal lemma is
\texttt{sum\_small\_le\_four\_sqrt} in
\path{MIPStarRE/LDT/MakingMeasurementsProjective/QXPLayer/TruncationCombinatorics.lean},
lines 164--175. It is accompanied by two auxiliary lemmas
\texttt{card\_mul\_sum\_small\_le} (lines 100--119) and
\texttt{card\_univ\_mul\_sum\_compl\_le} (lines 125--148).}

In the statement of the lemma, the overlaps are replaced by a function
$f\colon \alpha\to \mathbb{R}$ on a finite set $\alpha$. The subset $L\subseteq\alpha$
plays the role of the large overlaps, and $L^{\mathsf c}$ plays the role of
$\Small$. The hypotheses are $|L|=d$, $d < |\alpha|$,
$|\alpha| \le (1+2\sqrt\zeta)\,d$, the ordering condition
$f(s)\le f(l)$ for all $s\in L^{\mathsf c}$ and $l\in L$, the total estimate
$\sum_{x\in\alpha} f(x) \le 1+2\sqrt\zeta$, and
$0\le \zeta\le 1/4$. The conclusion is
\[
  \sum_{s\in L^{\mathsf c}} f(s) \le 4\sqrt\zeta.
\]
The proof does not need the hypothesis that every $f(x)$ is non-negative. It
uses only the ordering hypothesis, the total estimate, and the cardinality
relations; the sign of $f$ plays no role in the calculation.

\section{Comparison}

In the paper, the values $o_{a,i}$ are non-negative by construction. Thus any
abstract version which retains all paper-specific facts may include the
hypothesis $f(x)\ge 0$. The formal lemma proves the same inequality without that
hypothesis. It is therefore stronger than the natural abstracted statement with
non-negative $f$, while leaving the concrete estimate in the paper unchanged.

The difference does not affect soundness. The formal proof of the
orthogonalization lemma instantiates the combinatorial lemma with the actual
overlaps $o_{a,i}$, which are indeed non-negative. In that instantiation the
ordering and total-estimate hypotheses are verified from the properties of the
overlaps, and the lemma then supplies the needed bound on the sum over the small
entries.

\section{Relation with the blueprint}

The blueprint states the same abstract averaging lemma as
\path{lem:small-overlap-averaging} in
\cite[Chapter~\emph{Making measurements projective}]{MIPStarREBlueprint}.
\footnote{In the blueprint source consulted here, this is in
\path{blueprint/src/chapter/ch04_projective.tex}, lines 419--440.}
It takes $f:\alpha\to \mathbb{R}$ to be an arbitrary real-valued function and
does not require $f\ge 0$. Its hypotheses are the ordering condition, the total
estimate, the size constraints, and $0\le\zeta\le 1/4$, followed by the same
conclusion $\sum_{s\in L^{\mathsf c}}f(s)\le 4\sqrt\zeta$. Thus the
blueprint and the formal statement agree: both record the ordered
double-counting argument in a form which is more general than the concrete
overlap calculation in the paper.

\section{Conclusion}

There is no theorem-level gap. The formal lemma is a conservative strengthening
of the argument in the paper. The paper's proof of the
small-overlaps bound uses only the ordering hypothesis, the total estimate, and
the cardinality relations; it never invokes the nonnegativity of the overlaps
except through their definition. The formal development makes this explicit by
removing the nonnegativity condition from the statement. In the application
within the orthogonalization lemma, the stronger statement is specialized back to
the non-negative overlaps, so the formal soundness argument remains faithful to
the paper.

\bibliographystyle{alpha}
\bibliography{references}

\end{document}